---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

R package rankdist
====================

Implements distance based probability models for ranking data. 
    The supported models include Mallow's Phi-model (Kendall distance), Weighted Kendall distance model and Phi-Component model. Mixture models are also supported.
    
Examples
====================
Fit a single-cluster Mallow's Phi-model to APA election data.
```{r}
library(rankdist)
testctrl <- new("RankControlKendall")
testinit <- new("RankInit",param.init=list(1),modal_ranking.init=list(c(2,3,4,1,5)),clu=1L)
ken_c1 <- RankDistanceModel(apa_obj,testinit,testctrl)
```

Fit a three-cluster Weighted Kendall distance model to APA election data.
```{r}
testinit <- new("RankInit",param.init=list(rep(0.1,4),rep(0.1,4),rep(0.1,4)),modal_ranking.init=list(c(3,4,5,1,2),c(2,3,1,5,4),c(4,2,5,3,1)),clu=3L,p.init=rep(1,3)/3)
testctrl <- new("RankControlWeightedKendall")
# wken_c3 <- RankDistanceModel(apa_obj,testinit,testctrl)
```




